---
title: "Package Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25alexisbrown)
```

# Functions

## Birthday Problem Function

Calculates a probability scalar that 2 or more people share a birthday in a group of n people.

```{r}
birthday(25)
```

## Hypergeometric Simulation Function

Creates a bar plot of the distribution of number of successes over the hypergeometric simulation with number of iterations iter, population size N, number of successes r, and sample size n.

```{r}
myhyper(iter = 100, N =20, r =12, n =5)
```

## Bootleg Function

Creates a histogram of the bootstrap sample statistic with the confidence interval and point estimate labelled.

```{r}
myboot2(iter=10000,x=1:10,fun="mean",alpha=0.05,cx=1.5)
```


## Scatterhist Function

Creates a scatter plot of x vs y with marginal histograms.

```{r}
scatterhist(x = 1:10, y = 11:20)
```
